Automated Formal Synthesis of Digital Controllers for State-Space Physical Plants\thanks{Supported by EPSRC grant EP/J012564/1, ERC project 280053 (CPROVER) and the H2020 FET OPEN 712689 SC$^2$.}

### 2017-05-01 cav2017/cav2017.tex

Linear Time Invariant (LTI) models represent a broad class of dynamical
systems with significant impact in numerous application areas such as in life
sciences, robotics, and engineering~\cite{astrom1997computer,Franklin15}. 
The synthesis of controllers for LTI models is well understood, however the
use of digital control architectures adds new challenges due to the effects
of finite-precision arithmetic, time discretization, and quantization noise,
which are typically introduced by Analogue-to-Digital (ADC) and
Digital-to-Analogue (DAC) conversion.  While research on digital control is
well developed~\cite{astrom1997computer}, automated and sound control
synthesis is challenging, particularly when the synthesis objective goes
beyond classical stability.  There are recent methods for verifying
reachability properties of a given controller~\cite{FLD+11,Fre05}. 
However, these methods have not been generalized to control synthesis. 
We~remark that a synthesis algorithm that guarantees satability does not
ensure safety: the system might transitively visit an unsafe state that
results in an unrecoverable failure.

@@

We provide experimental results showing that both approaches are able to
efficiently synthesize stable and safe controllers for a set of intricate
physical plant models taken from the digital control literature: the median
run-time for our benchmark set is $7.9$ seconds, and most controllers can be
synthesized in less than $17.2$ seconds.  We further show that, in a direct
comparison, the abstraction-based approach (second) lowers the median
run-time of our benchmarks by a factor of seven over the first approach
based on the unfolding of the dynamics.

@@

\begin{enumerate}
%
\item  We compute state-feedback controllers that are provably stable and in
  addition guaranteee a given safety property.  Existing methods for
  controller synthesis rely on transfer function representations, which are
  insufficient to prove safety requirements.
%
\item We give two novel algorithms: the first, na\"ive one, relies on
  an unfolding of the dynamics up to a completeness threshold, while the
  second one is abstraction-based and leverages abstraction refinement and
  acceleration to improve scalability while retaining soundness.  Both
  approaches provide sound synthesis of state-feedback systems and consider
  the various sources of imprecision in the implementation of the control
  algorithm and in the modeling of plant.
%
\item We develop a model for different sources of quantization errors and
  their effect on reachability properties.  We give bounds that ensure the
  safety of our controllers in a hybrid continuous-digital domain.
%
\end{enumerate}

>>>>

Linear Time Invariant (LTI) models represent a broad class of dynamical
systems with significant impact in numerous application areas such as in life
sciences, robotics, and engineering~\cite{astrom1997computer,Franklin15}. 
The synthesis of controllers for LTI models is well understood, however the
use of digital control architectures adds new challenges due to the effects
of finite-precision arithmetic, time discretization, and quantization noise,
which are typically introduced by Analogue-to-Digital (ADC) and
Digital-to-Analogue (DAC) conversion.  While research on digital control is
well developed~\cite{astrom1997computer}, automated and sound control
synthesis is challenging, particularly when the synthesis objective goes
beyond classical stability.  There are recent methods for verifying
reachability properties of a given controller~\cite{FLD+11,Fre05}. 
However, these methods have not been generalized to control synthesis. 
We~remark that a synthesis algorithm that guarantees stability does not
ensure safety: the system might transitively visit an unsafe state that
results in an unrecoverable failure.

@@

We provide experimental results showing that both approaches are able to
efficiently synthesize stable and safe controllers for a set of intricate
physical plant models taken from the digital control literature: the median
run-time for our benchmark set is $7.9$ seconds, and most controllers can be
synthesized in less than $17.2$ seconds.  We further show that, in a direct
comparison, the abstraction-based approach (i.e., the second approach) lowers the median
run-time of our benchmarks by a factor of seven over the first approach
based on the unfolding of the dynamics.

@@

\begin{enumerate}
%
\item  We compute state-feedback controllers that are provably stable and in
  addition guaranteee a given safety property.  Existing methods for
  controller synthesis rely on transfer function representations, which are
  insufficient to prove safety requirements.
%
\item We give two novel algorithms: the first, na\"ive one, relies on
  an unfolding of the dynamics up to a completeness threshold, while the
  second one is abstraction-based and leverages abstraction refinement and
  acceleration to improve scalability while retaining soundness.  Both
  approaches provide sound synthesis of state-feedback systems and consider
  the various sources of imprecision in the implementation of the control
  algorithm and in the modeling of the plant.
%
\item We develop a model for different sources of quantization errors and
  their effect on reachability properties.  We give bounds that ensure the
  safety of our controllers in a hybrid continuous-digital domain.
%
\end{enumerate}
